---
title: "Metallica Concerts"
author: "Kevin Gilds, MPA"
date: "September 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(tidytext)
library(knitr)
library(kableExtra)
library(ggplot2)
library(wordcloud)
library(DT)

```

# Metallica Concerts

I was looking for something to do while hunkering down during Hurrican Irma. I love Metallica and coding in R. I am currently writing this September 10, 2017 in Bartow, FL. 


```{r tours, echo=TRUE}
tours <- read.delim("metallica_cours.txt") %>%
	rename("Tour_Name" = "Tour_.Name")

#kable(tours)
```

```{r setlist, echo=TRUE}
setlist <- read.delim("setlist.txt")

#kable(setlist)
```


```{r setlist_tour_join, echo=TRUE}
setlist_tour <- inner_join(setlist, tours, by="id")

#kable(setlist_tour)
```



I have attended eight (8) Metallica concerts from 1989 through 2017. Metallica makes available their sets list from their shows at [Met on Tour]("https://www.metallica.com/tour/past"). The only show where I had to use a different data sources is the 1989 show in Cedar Rapids, Iowa. I used this 
[SetList]("https://www.setlist.fm/setlist/metallica/1989/hilton-coliseum-ames-ia-33d6d411.html") from Ames, Iowa as a proxy and this list matches my memory. Here is the set list from each show using a datatable. 
```{r setlist_tour, echo=TRUE}
setlist_tour <- setlist_tour %>%
	select(3, 2, 6:9) 

datatable(setlist_tour)




```

## Song Count by City

I have seen more Metallica perform the most songs in Cedar Rapids, Iowa and a close second is Tampa, FL. 


```{r}

setlist_tour_tbl <- tours %>%
	group_by(Tour_Name) %>%
	select(5:6)


kable(setlist_tour_tbl)

```


```{r}

setlist_tour_city <- setlist_tour %>%
     count(City)


kable(setlist_tour_city)

```





From this set list of eight tours some song titles are repeated and on average song_titles repeat 2.3 times.

```{r song_count_avg, echo=TRUE}
song_count_avg <- setlist_tour %>%
	count(song_title) %>%
	summarise(song = mean(n))


kable(song_count_avg)

```

Below is a graph of the song_titles I have heard more than once. At first, glance, I was surprised that I had not seen *Master of Puppets* eight times. I checked the data and it occurred to me during the [*M2K*]("https://www.metallica.com/tour/10360") Tour in St. Petersburg that Metallica performed *Masterarium*--a mix of Master of Puppets and Welcome Home Sanitarium. A fantastic performance. 



```{r song_count, echo=FALSE}
song_count <- setlist_tour %>%
	count(song_title, sort = TRUE)
	

#kable(song_count)



setlist_tour %>%
	count(song_title) %>%
	filter(n >2) %>%
	mutate(song_title = reorder(song_title, n)) %>% #this changes the order of the graph
	ggplot(aes(song_title, n)) +
	geom_col() +
	xlab(NULL) +
	coord_flip()




```



```{r song_coung_avg}

```



("https://stackoverflow.com/questions/26114525/r-how-to-count-how-many-values-per-level-in-a-given-factor")

This article helped me figure out to perform a count using factors. 

## Number of Song performed

On average, Metallica performed 18 songs when I went to see them. 

```{r}
tour_count_avg <- setlist_tour %>%
	group_by(Tour_Name) %>%
	summarise(song_title = length(song_title)) %>%
	summarise(song_title= mean(song_title))

kable(tour_count_avg)

```

Here is a breakdown of the number of songs played during each tour stop. 

```{r}

song_count_tour <- setlist_tour %>%
	group_by(Tour_Name) %>%
	summarise(song_title = length(song_title))
	
kable(song_count_tour)
	


```


### Wordcloud Mess

This stackover flow question and answer helped me with this WordCloud. At least it helped me plot all the songs. 

("https://stackoverflow.com/questions/27981651/text-wordcloud-plotting-error")


```{r}

song_count_wc <- setlist_tour %>%
	count(song_title) %>%
	with(wordcloud(song_title, n, scale = c(3, 0.1)))
	





```
```




